A geographic routing approach for IPv6 in low-powered and lossy large-scale wireless networks

### 2015-03-27 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
adição de biografias

%Carlos Henrique Barriquello is an Adjunct Professor in the Electronics and Computing Department at the Federal University of Santa Maria, Brazil, since 2012. He received the B.Sc., M.Sc. and Ph.D. degrees in electrical engineering from Federal University of Santa Maria in 2007, 2009 and 2012, respectively. His research interests include embedded systems and wireless sensor/actuator networks.

>>>>

\noindent {\bf Carlos Henrique Barriquello} is an Adjunct Professor in the Electronics and Computing Department at the Federal University of Santa Maria, Brazil, since 2012. He received the B.Eng., M.Eng. and Ph.D. degrees in electrical engineering from Federal University of Santa Maria in 2007, 2009 and 2012, respectively. His research interests include embedded systems and wireless sensor/actuator networks.

\noindent {\bf Alexandre Campos}, B.Eng.1981, M.Eng. 1986 and Ph.D. 1994, all in electrical engineering. He has a broad experience on electrical and computer engineering, specially on: high power electronics; static power converters; electronic ballasts; intelligent lightning systems; embedded systems; signal processing. He is also interested in STEM education methodology. He is a CEFE and TRIZ specialist.
